---
title: "Batch folding analysis"
output: html_document
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
Sys.setenv(RETICULATE_PYTHON = "/home/joris/miniconda3/bin/python")

pacman::p_load(magrittr,dplyr,ggplot2, RCy3, reticulate)

```

## Data import

```{r data import}
setwd("~/scratch/folding_comparision/")
comparisons <- read.csv2("folding_fatcat_output_inc_rbp1.tsv",
                         sep='\t', stringsAsFactors = F)
comparisons$opt.rmsd %<>%as.numeric
comparisons$P.value %<>% as.numeric
comparisons$Identity %<>% as.numeric

```

## Pvalue adjustment

```{r}
adj_factor <- comparisons$Subject %>% 
  unique() %>% length
comparisons$P.adjusted <- as.numeric(comparisons$P.value) * adj_factor

comparisons.filtered <- comparisons %>% 
  filter(P.adjusted <=0.05)
```

## Plot Identity All vs significant only

```{r}
All_identity <- cbind(as.numeric(comparisons$Identity), rep("All",times=nrow(comparisons)))
sig_identity <- cbind(comparisons.filtered$Identity, rep("Significant only", times=nrow(comparisons.filtered)))

Identities <- rbind(All_identity, sig_identity) %>% data.frame
colnames(Identities) <- c("Identity","Set")
Identities$Identity %<>% as.numeric

All_rmsd <- cbind(as.numeric(comparisons$opt.rmsd), rep("All",times=nrow(comparisons)))
sig_rmsd <- cbind(comparisons.filtered$opt.rmsd, rep("Significant only", times=nrow(comparisons.filtered)))
RMSDs <- rbind(All_rmsd, sig_rmsd) %>% data.frame(stringsAsFactors = F)
colnames(RMSDs) <- c("RMSD", "Set")
RMSDs$RMSD %<>% as.numeric

Identities %>% 
  ggplot +
  geom_density(
    aes(
      x=Identity,
      fill=Set
      ),
    alpha=0.5
    ) +
  scale_x_continuous(name='Percent Sequence Identity',breaks=c(seq(1,30,2),seq(30,50,5),80)) +
  ggtitle("Sequence Identity")
  
```

## Sanity check plot Score vs length

```{r}
# Sanity check
plot(comparisons.filtered$score, comparisons.filtered$align.len)
```

## Vulcano plot Identity vs P-value

```{r}
plot.df <- cbind(
  as.numeric(comparisons$Identity),
  -1*log10(as.numeric(comparisons$P.adjusted+0.00000000001))
)

plot.df%<>% as.data.frame()
colnames(plot.df) <- c("X","Y")

pvalue_log <- -1*log10(0.05)
plot.df %>% 
  ggplot +
  geom_point(
    aes(
      x = X,
      y = Y, 
      colour = Y >= pvalue_log
      )
    ) +
  scale_colour_manual(
    name = "Significant", 
    values = setNames(c("blue","black"), 
                      c(T,F)
                      )
    )+
  xlab("Percent Identity") +
  ylab("-Log10(pvalue)") +
  ggtitle("Identity vs P-value") +
  theme_bw() 

ggsave(
  filename = 'identity_vs_pvalue.pdf',
  device = 'pdf')
ggsave(
  filename = 'identity_vs_pvalue.png',
  device = 'png')
```

## Gpal Effectors

```{r}
effector_ids_gpal <- read.csv(
  "gpal_effector_lookup_table.txt", 
  sep = '\t',header = F)
colnames(effector_ids_gpal) <- c("ID",'Family')

gpal_effector_matches <- comparisons.filtered %>% 
  filter(Subject %in% effector_ids_gpal$ID)


effector_family_names <- effector_ids_gpal %>% 
  filter(ID %in% gpal_effector_matches$Subject)

write.csv(
  gpal_effector_matches, 
  file='gpal_effectors_matches.csv', 
  quote = F, 
  )

lookup_effector_family <- function(fam_name){
  print(fam_name)
  table.filter <- gpal_effector_matches %>% 
  filter(Subject %in% effector_family_names[which(effector_family_names$Family ==fam_name), "ID"])
  
  table.filter$Subject %>% 
    unique %>% 
    length %>% 
    print
  
  table.filter$Query %>% 
    unique %>% 
    length %>% 
    print
  
  table.filter %>% 
    .[,'Identity'] %>% 
    mean %>% 
    print
  
  return(table.filter)
}

gland5_table  <- lookup_effector_family('GLAND5_CDS.fasta')
sprysec_table <- lookup_effector_family('SPRYSEC_CDS.fasta')
vap_table     <- lookup_effector_family('VAP_CDS.fasta')

 

```

## Playground

```{r}

##########################
table(comparisons.filtered$Query) %>% 
  sort(decreasing = T) %>%
  #density %>% 
  plot(type='l',xaxt="n")


subset <- comparisons.filtered %>% 
  filter(Query=="g8298.pdb") %>% 
  filter(opt.rmsd <=0.8)


plot(
  subset$Identity, 
  subset$opt.rmsd, 
  main="Identity vs RMSD",
  xlab="Percent Identity",
  ylab="Optimised RMSD")


subset$opt.rmsd %>% density %>%  plot(main="Optomised RMSD", xlab='RMSD')


sprysec_example = "Gpal_D383_g01418.pdb"
sprysec_example2 = "Gpal_D383_g12494.pdb"
subset_sprysec <- comparisons.filtered %>% 
  filter(Subject==sprysec_example2)


subset_sprysec$opt.rmsd %>% density %>%  plot(main="Optomised RMSD", xlab='RMSD')
```

# Heatmap

```{r}
library(gplots)
pvalue_matrix <- comparisons %>% 
  .[,c("Query","Subject","P.adjusted")] %>%
  reshape(
    direction = 'wide', 
    idvar="Query", 
    timevar = "Subject"
    )  

rownames(pvalue_matrix) <- pvalue_matrix[,1]
pvalue_matrix[,1] <- NULL

d <- pvalue_matrix %>% 
  as.matrix %>% 
  add(0.0000001) %>% 
  log10 %>% 
  multiply_by(-1)

heatmap.2(
  d,
  trace="none"
  )

```

# Cytoscape export


### Gpal Functional Annotations
```{r}
reticulate::source_python("misc.py")
library(stringr)
annotations_pal <- read.csv2(
  "/mnt/nemahomes/steen176/Genomes/Annotations/G_pallida_annotations_onlyt1pruned.csv",
  sep='\t') 

rownames(annotations_pal) <- annotations_pal$SeqName

gpal_nodes <- cbind(
  comparisons.filtered$Subject, 
  rep(
    "Gpal", times = length(comparisons.filtered$Subject)
    )
  )
colnames(gpal_nodes) <- c('id','species')

gpal_ids_clean <- strip_pdb_ids(gpal_nodes[,'id'])

gpal_nodes %<>% cbind(., 
                      annotations_pal[
                        gpal_ids_clean,
                        c(
                          "Description",
                          "GO.IDs", 
                          "Enzyme.Names", 
                          "InterPro.GO.Names", 
                          "InterPro.IDs"
                          )
                        ]
                      )



```

### Mchit Import Functional Annotations
```{r}
annotations_mchit <- read.csv2(
  "/mnt/dataHDD/scratch/chitwoodi_genomes/annotation/omicsbox_table_onlyt1.txt",
  sep = '\t'
  )

rownames(annotations_mchit) <- annotations_mchit$SeqName

mchit_nodes <- cbind(
  comparisons.filtered$Query, 
  rep(
    "Mchit", times = length(comparisons.filtered$Query)
    )
  )
colnames(mchit_nodes) <- c('id','species')

mchit_ids_clean <- strip_pdb_ids(mchit_nodes[,'id'])

mchit_nodes %<>% cbind(., 
                      annotations_mchit[
                        mchit_ids_clean,
                        c(
                          "Description",
                          "GO.IDs", 
                          "Enzyme.Names", 
                          "InterPro.GO.Names", 
                          "InterPro.IDs"
                          )
                        ]
                      )
```

### Format Node and Edge data frames

```{r format node edges}
library(RCy3)

nodes <- rbind(
  gpal_nodes,
  mchit_nodes
  ) %>% 
  data.frame

edges <- comparisons.filtered[,c('Query',"Subject", "Identity",'P.adjusted')] %>% data.frame
colnames(edges) <- c("source","target", "Identity",'P.adjusted')
write.csv2(edges, file = 'cytoscape_edges.csv')


```

### Export Cytoscape

Inside cytoscape I run the clustering algorithm 'fast greedy' to get cluster number assigned to the nodes

```{r export cytoscape}
createNetworkFromDataFrames(nodes,edges)

style.name = "myStyle"
defaults <- list(NODE_SHAPE="circle",
                 NODE_SIZE=30,
                 EDGE_TRANSPARENCY=30,
                 NODE_LABEL_POSITION="W,E,c,0.00,0.00")

nodeLabels <- mapVisualProperty('node label','id','p')
nodeFills <- mapVisualProperty('node fill color','species','d',c("Gpal","Mchit"), c("#FF9900","#66AAAA"))
edgeWidth <- mapVisualProperty('edge width','Identity','p')


createVisualStyle(style.name, defaults, list(nodeFills,edgeWidth))
setVisualStyle(style.name)

```

## Merge cluster number and Identity/pvalue

```{r}

reticulate::source_python('parse_cluster_info.py')
cluster_identities <- get_cluster_identities()

cluster_identities$Identity %<>% 
  sapply(function(x) sub(pattern = ",",replacement = '.',x = x)) %>%   as.numeric()
cluster_identities$P.adjusted %<>% 
  sapply(function(x) sub(pattern = ",",replacement = '.',x = x)) %>%   as.numeric()
```

```{r}
cluster_sizes <- cluster_identities$Cluster %>% table
cluster_sizes_pruned <- cluster_sizes %>%  
  magrittr::is_less_than(2) %>% 
  `!` %>%  
  which %>% 
  names

cluster_identities_pruned <- cluster_identities %>% 
  filter(Cluster %in% cluster_sizes_pruned)

#rownames(cluster_identities_pruned) <- cluster_identities_pruned$Cluster
```

## Plot identity vs pvalue -\> per cluster

```{r}
cluster_identities_pruned %>% 
  ggplot + 
  geom_point(aes(x=Identity, y = -1*log10(P.adjusted+0.000001)))  +
  facet_wrap(~Cluster)
```

```{r}
clusterNames <- unique(cluster_identities$Cluster)
cluster_table <- read.csv2('cytoscape_clusters.csv', sep=',')


get_most_occuring <- function(var,species,cl_clean){
  descriptions <- cluster_table %>%
    filter(X__fastGreedyCluster== cl_clean & species==species) %>% 
    .[[var]]
  
  descriptions[!descriptions %in% c('---NA---','unnamed protein product','no IPS match','no GO terms')] %>% 
    table %>% 
    sort(decreasing = T) %>% .[1] %>% 
    names %>% 
    return
}


cluster_descriptions <- sapply(clusterNames, function(cluster){
  cl_clean <- sub('Cl','',cluster)
  avg_cluster_identity <- cluster_identities %>%
    filter(Cluster == cluster) %>%
    .$Identity %>%
    mean
  
  description_gpal <- get_most_occuring('Description', 'Gpal',cl_clean)
  GOnames_gpal <- get_most_occuring('InterPro.GO.Names', 'Gpal',cl_clean)
  
  description_mchit <- get_most_occuring('Description', 'Mchit',cl_clean)
  
  GOnames_mchit <- get_most_occuring('InterPro.GO.Names', 'Mchit',cl_clean)
  
  return(
    c(
      cluster,
      avg_cluster_identity,
      description_gpal, 
      description_mchit,
      GOnames_gpal,
      GOnames_mchit
      )
    )
})  %>% do.call(rbind.data.frame, .)

colnames(cluster_descriptions) <- c(
  "Cluster", 
  "AvgClusterIdentity",
  "gpalDescription",
  "mchitDescription",
  "gpalGOnames",
  "mchitGOnames"
  )
cluster_descriptions$AvgClusterIdentity %<>% as.numeric
View(cluster_descriptions)
```
